\startsection[title={CSESS Orientation Night}][
date={\date[d=9, m=9, y=2023][event]},
pic={Nelson (IV), Sam (EV), Stan (E Sec)}]

\subsection{Main PIC(s)}
\namedstructureuservariable{section}{pic}

\subsection{Objectives}
\startitemize
\item To introduce the Society and the Executive Committee to new students.
\item To promote activities and welfare provided by the Society.
\item To reunite students who participated in the Orientation Camp.
\item To enable students who cannot participate in the Orientation Camp to meet like-minded friends.
\stopitemize

\subsection{Details}
\starttabulate[|rB|l|]
\NC Date
\NC \namedstructureuservariable{section}{date} \NR
\NC Time
\NC 18:00\endash22:00 \NR
\NC Venue
\NC Partyroom \NR
\NC Audience
\NC Participants of Orientation Camp and Freshmen \NR
\NC Est. Participants
\NC 20 \NR
\NC Budget (\$)
\NC 1000 \NR
\NC Fee (\$)
\NC 70 \NR
\stoptabulate

\subsection{Schedule}

\setupTABLE[c][1][width=0.75in]
\setupTABLE[c][2][width=1in]
\setupTABLE[c][3][width=3in]
\setupTABLE[c][4][width=1.25in]
\bTABLE
\bTABLEhead

\bTR\bTH    \bf{DTF}
\eTH\bTH    \bf{Finish Date}
\eTH\bTH    \bf{Task}
\eTH\bTH    \bf{PIC(s)}
\eTH\eTR

\eTABLEhead
\bTABLEbody

\bTR\bTD 3\endash1
\eTD\bTD 12\high{th} August
\eTD\bTD Book venue.
\eTD\bTD Samuel (In Sec)
\eTD\eTR

\bTR\bTD 4\endash2
\eTD\bTD 27\high{th} August
\eTD\bTD Design Poster.
\eTD\bTD Cindy (PP Sec)
\eTD\eTR

\bTR\bTD 3\endash1
\eTD\bTD 27\high{th} August
\eTD\bTD Confirm Rundown Details.
\eTD\bTD Nelson (IV) \\ Sam (EV)
\eTD\eTR

\bTR\bTD 3\endash1
\eTD\bTD 27\high{th} August
\eTD\bTD Prepare Games.
\eTD\bTD Stan (E Sec) \\ Paddy (Fin Sec) \\ Jacky (A Sec)
\eTD\eTR

\bTR\bTD 4\endash2
\eTD\bTD 27\high{th} August
\eTD\bTD Prepare Equipment.
\eTD\bTD Stan (E Sec) \\ Paddy (Fin Sec) \\ Jacky (A Sec)
\eTD\eTR

\bTR\bTD 1
\eTD\bTD 31\high{st} August
\eTD\bTD Final Rehearsal.
\eTD\bTD All
\eTD\eTR

\bTR\bTD 14\endash7\endash1
\eTD\bTD 31\high{st} August
\eTD\bTD Promote.
\eTD\bTD Samuel (In Sec) \\ Cindy (PP Sec)
\eTD\eTR

\eTABLEbody
\eTABLE

\subsection{Equipment \& Consumables}
\starttabulate[|l|l|]
\NC\setff{smallcaps}Equipment\NC\NR
\HL
\NC Society Banner          \NC $\times$ 1  \NR
\NC Camera                  \NC $\times$ 1  \NR
\NC Pens                    \NC $\times$ 10 \NR
\HL
\NR
\NC\setff{smallcaps}Consumables\NC\NR
\HL
\NC Large Pizza             \NC $\times$ 5      \NR
\NC Soft Drinks             \NC 6 $\times$ 6 $\times$ 315ml \NR
\NC Participant List        \NC $\times$ 1      \NR
\NC Tissue (Boxes)          \NC $\times$ 5      \NR
\NC Trash Bags              \NC $\times$ 5      \NR
\NC Paper                   \NC $\times$ 100    \NR
\HL
\stoptabulate

\subsection{Rundown of Function}

\setupTABLE[c][1][width=1.25in]
\setupTABLE[c][2][width=3.5in]
\setupTABLE[c][3][width=1.25in]
\bTABLE
\bTABLEhead

\bTR\bTH    \bf{Time}
\eTH\bTH    \bf{Description}
\eTH\bTH    \bf{PIC(s)}
\eTH\eTR

\eTABLEhead
\bTABLEbody

\bTR\bTD 18:00\endash18:15
\eTD\bTD Set Up Venue.
\eTD\bTD Any 4
\eTD\eTR

\bTR\bTD 18:15\endash18:30
\eTD\bTD Meet Up and Travel to Venue.
\eTD\bTD Any 4
\eTD\eTR

\bTR\bTD 18:30\endash18:40
\eTD\bTD Introduction and Divide in Groups.
\eTD\bTD All
\eTD\eTR

\bTR\bTD 18:40\endash19:00
\eTD\bTD Warm-up Games (in Small Groups) and Food Ordering.
\eTD\bTD Any 7+1
\eTD\eTR

\bTR\bTD 19:00\endash20:00
\eTD\bTD Mass Games.
\eTD\bTD All
\eTD\eTR

\bTR\bTD 20:00\endash20:30
\eTD\bTD Singing Contest.
\eTD\bTD All
\eTD\eTR

\bTR\bTD 20:30\endash21:30
\eTD\bTD Dinner.
\eTD\bTD Any 2
\eTD\eTR

\bTR\bTD 21:30\endash21:45
\eTD\bTD Take Photos.
\eTD\bTD All
\eTD\eTR

\bTR\bTD 21:45\endash22:00
\eTD\bTD Clean Up.
\eTD\bTD All
\eTD\eTR

\eTABLEbody
\eTABLE

\subsection{Remarks}
\startitemize
\item Special arrangement during Inclement Weather or emergency: \\
If any of the Rainstorm Warnings or Tropical Cyclone Warning Signal No.3 or above is hoisted, the function will be either postponed or canceled. Participants will be notified of further arrangements through email.
\item There will be both Chinese and English MCs if there are non cantonese speaking participants.
\stopitemize

\stopsection
\pagebreak
