\startsection[title={CSESS Orientation Week}][
date={4\high{th} September \endash\ 14\high{th} September, 2023 (Monday \endash\ Thursday)},
pic={Terry (P), Samuel (In Sec), Stan (E Sec)}]

\subsection{Main PIC(s)}
\namedstructureuservariable{section}{pic}

\subsection{Objectives}
\startitemize
\item Attract non-members to join the Society.
\item Promote and sell Society products.
\item Promote upcoming activities of the Society.
\item To recruit sports team members.
\stopitemize

\subsection{Details}
\starttabulate[|rB|l|]
\NC Date
\NC \namedstructureuservariable{section}{date} \NR
\NC Time
\NC 10:00\endash18:00 \NR
\NC Venue
\NC Atrium \NR
\NC Audience
\NC Freshmen and Society Members \NR
\NC Est. Participants
\NC N/A \NR
\NC Fee (\$)
\NC Discount (Members) or Standard (Non-Members) \NR
\stoptabulate

\subsection{Schedule}

\setupTABLE[c][1][width=0.75in]
\setupTABLE[c][2][width=1in]
\setupTABLE[c][3][width=3in]
\setupTABLE[c][4][width=1.25in]
\bTABLE
\bTABLEhead

\bTR\bTH    \bf{DTF}
\eTH\bTH    \bf{Finish Date}
\eTH\bTH    \bf{Task}
\eTH\bTH    \bf{PIC(s)}
\eTH\eTR

\eTABLEhead
\bTABLEbody

\bTR\bTD N/A
\eTD\bTD 28\high{th} August
\eTD\bTD Schedule of PICs for the Counter.
\eTD\bTD Terry (P) \\ Samuel (In Sec) \\ Cindy (PP Sec)
\eTD\eTR

\bTR\bTD N/A
\eTD\bTD 28\high{th} August
\eTD\bTD Make Products.
\eTD\bTD Terry (P) \\ Nelson (IV) \\ Sam (EV)
\eTD\eTR

\bTR\bTD N/A
\eTD\bTD 28\high{th} August
\eTD\bTD Noticeboard Decorations.
\eTD\bTD Cindy (PP Sec)
\eTD\eTR

\bTR\bTD N/A
\eTD\bTD 28\high{th} August
\eTD\bTD Counter Decorations.
\eTD\bTD Nelson (IV) \\ Sam (EV) \\ Cindy (PP Sec)
\eTD\eTR

\eTABLEbody
\eTABLE

\subsection{Equipment \& Consumables}
\starttabulate[|l|l|]
\NC\setff{smallcaps}Equipment\NC\NR
\HL
\NC Color Paper \NC $\times$ 4 \NR
\NC Society Signboard \NC $\times$ 1 \NR
\NC Scissors \NC $\times$ 4 \NR
\NC Tablecloth \NC $\times$ 1 \NR
\NC Noticeboard \NC $\times$ 2 \NR
\NC Piggy Bank \NC $\times$ 1 \NR
\NC Society Chop \NC $\times$ 1 \NR
\NC Pens \NC $\times$ 2 \NR
\NC Member List \NC $\times$ 1 \NR
\NC Cheque Book \NC $\times$ 1 \NR
\NC Banner \NC $\times$ 1 \NR
\HL
\stoptabulate

\subsection{Rundown of Function}

\setupTABLE[c][1][width=1.25in]
\setupTABLE[c][2][width=3.5in]
\setupTABLE[c][3][width=1.25in]
\bTABLE
\bTABLEhead

\bTR\bTH    \bf{Time}
\eTH\bTH    \bf{Description}
\eTH\bTH    \bf{PIC(s)}
\eTH\eTR

\eTABLEhead
\bTABLEbody

\bTR\bTD 09:45\endash10:00
\eTD\bTD Open Counter.
\eTD\bTD Any 4
\eTD\eTR

\bTR\bTD 10:00\endash18:00
\eTD\bTD Exist.
\eTD\bTD Any 4
\eTD\eTR

\bTR\bTD 18:00\endash18:10
\eTD\bTD Close Counter.
\eTD\bTD Any 4
\eTD\eTR

\eTABLEbody
\eTABLE

\stopsection
\pagebreak
