\startsection[title={CSESS Sub-Committee Function}][
date={\date[d=15, m=9, y=2023][event]},
pic={Terry (P)}]

\subsection{Main PIC(s)}
\namedstructureuservariable{section}{pic}

\subsection{Objectives}
\startitemize
\item To let our members experience what it would be like being the Executive Committee.
\item To introduce the Society and the Executive Committee to freshmen.
\item To assemble the successor cabinet of session 2024\endash2025.
\stopitemize

\subsection{Details}
\starttabulate[|rB|l|]
\NC Date
\NC \namedstructureuservariable{section}{date} \NR
\NC Time
\NC 19:30 \NR
\NC Venue
\NC Computer Lab, Room 4214 \NR
\NC Audience
\NC Freshmen \NR
\NC Est. Participants
\NC 20 \NR
\NC Budget (\$)
\NC 200 (If Not Profitable) \NR
\NC Fee (\$)
\NC TBD \NR
\stoptabulate

\subsection{Schedule}

\setupTABLE[c][1][width=0.75in]
\setupTABLE[c][2][width=1in]
\setupTABLE[c][3][width=3in]
\setupTABLE[c][4][width=1.25in]
\bTABLE
\bTABLEhead

\bTR\bTH    \bf{DTF}
\eTH\bTH    \bf{Finish Date}
\eTH\bTH    \bf{Task}
\eTH\bTH    \bf{PIC(s)}
\eTH\eTR

\eTABLEhead
\bTABLEbody

\bTR\bTD 0
\eTD\bTD 6\high{th} September
\eTD\bTD Meet With Participants To Discuss the Form of Function Day.
\eTD\bTD Terry (P) \\ Nelson (IV) \\ Sam (EV)
\eTD\eTR

\bTR\bTD 5
\eTD\bTD 8\high{th} September
\eTD\bTD Promotion Poster.
\eTD\bTD Terry (P) \\ Samuel (In Sec) \\ Cindy (PP Sec)
\eTD\eTR

\bTR\bTD 5
\eTD\bTD 8\high{th} September
\eTD\bTD Promotion Video.
\eTD\bTD Terry (P) \\ Samuel (In Sec) \\ Cindy (PP Sec)
\eTD\eTR

\bTR\bTD 0
\eTD\bTD 15\high{th} September
\eTD\bTD Assist With the Work of Sub-Committee.
\eTD\bTD All
\eTD\eTR

\eTABLEbody
\eTABLE

\pagebreak
\subsection{Rundown of Function}

\setupTABLE[c][1][width=1.25in]
\setupTABLE[c][2][width=3.5in]
\setupTABLE[c][3][width=1.25in]
\bTABLE
\bTABLEhead

\bTR\bTH    \bf{Time}
\eTH\bTH    \bf{Description}
\eTH\bTH    \bf{PIC(s)}
\eTH\eTR

\eTABLEhead
\bTABLEbody

\bTR\bTD 6\high{th} September \\ 18:00\endash19:00
\eTD\bTD Icebreaking Games.
\eTD\bTD Terry (P) \\ Samuel (In Sec) \\ Stan (E Sec)
\eTD\eTR

\bTR\bTD 6\high{th} September \\ 19:00\endash20:00
\eTD\bTD Discussion of Function Day Topic.
\eTD\bTD Terry (P) \\ Samuel (In Sec) \\ Stan (E Sec)
\eTD\eTR

\bTR\bTD 6\high{th} September \\ 20:00\endash20:15
\eTD\bTD Partition of Function Team and Promo Team.
\eTD\bTD Terry (P) \\ Samuel (In Sec) \\ Stan (E Sec)
\eTD\eTR

\eTABLEbody
\eTABLE

\stopsection
\pagebreak
