\section{CSE Annual Dinner}

\subsection{Main PIC(s)}
Terry (P), Jacky (A Sec)

\subsection{Objectives}
\startitemize
\item To provide entertainment and a fun night out for members and guests, and to create a positive and memorable experience for everyone involved.
\item To provide an opportunity for members to network and build relationships with each other.
\item To celebrate its achievements over the past year.
\stopitemize

\subsection{Details}
\starttabulate[|rB|l|]
\NC Date
\NC 11\high{th} February, 2024 (Sunday) \NR
\NC Time
\NC 18:30\endash20:30 \NR
\NC Venue
\NC LG7 \NR
\NC Audience
\NC Students and CSE Department Staff \NR
\NC Est. Participants
\NC 90\endash100 \NR
\NC Fee (\$)
\NC TBD; Sponsored by Department \NR
\stoptabulate

\subsection{Schedule}

\setupTABLE[c][1][width=0.75in]
\setupTABLE[c][2][width=1in]
\setupTABLE[c][3][width=3in]
\setupTABLE[c][4][width=1.25in]
\bTABLE
\bTABLEhead

\bTR\bTH    \bf{DTF}
\eTH\bTH    \bf{Finish Date}
\eTH\bTH    \bf{Task}
\eTH\bTH    \bf{PIC(s)}
\eTH\eTR

\eTABLEhead
\bTABLEbody

\bTR\bTD N/A
\eTD\bTD 11\high{th} December
\eTD\bTD Confirm Details With the Department.
\eTD\bTD Jacky (A Sec)
\eTD\eTR

\bTR\bTD N/A
\eTD\bTD 11\high{th} December
\eTD\bTD Check Equipment and Material With the Department.
\eTD\bTD Jacky (A Sec)
\eTD\eTR

\bTR\bTD 1
\eTD\bTD 11\high{th} December
\eTD\bTD Book Venue.
\eTD\bTD Jacky (A Sec)
\eTD\eTR

\bTR\bTD 1
\eTD\bTD 5\high{th} February
\eTD\bTD Ask Department To Send Reminder Email.
\eTD\bTD Jacky (A Sec)
\eTD\eTR

\bTR\bTD 10, 1
\eTD\bTD 5\high{th} February
\eTD\bTD Design Photo Props and Poster.
\eTD\bTD Samuel (In Sec) \\ Cindy (PP Sec) \\ Jacky (A Sec)
\eTD\eTR

\bTR\bTD 10, 1
\eTD\bTD 5\high{th} February
\eTD\bTD Buy Nametags and Boutonnière.
\eTD\bTD Samuel (In Sec) \\ Cindy (PP Sec) \\ Jacky (A Sec)
\eTD\eTR

\bTR\bTD 1
\eTD\bTD 5\high{th} February
\eTD\bTD Print Poster and Stick Poster.
\eTD\bTD Stan (E Sec)
\eTD\eTR

\eTABLEbody
\eTABLE

\subsubsection{Equipment \& Consumables}
\starttabulate[|l|l|]
\NC\setff{smallcaps}Equipment\NC\NR
\HL
\NC Society Signboard \NC $\times$ 1 \NR
\NC Farewell Video \NC $\times$ 1 \NR
\NC Backdrop \NC $\times$ 1 \NR
\NC Notice Boards \NC $\times$ 2 \NR
\NC Photo Props \NC $\times$ 7 \NR
\NC Cameras \NC $\times$ 2 \NR
\NC Nametags \NC $\times$ 20 \NR
\NC Boutonnière \NC $\times$ 20 \NR
\HL
\NR
\NC\setff{smallcaps}Consumables\NC\NR
\HL
\NC Letter Balloon \NC $\times$ 15 \NR
\NC Luck Draw Gifts \NC $\times$ 4 \NR
\NC Tape \NC $\times$ 2 \NR
\NC Scissors \NC $\times$ 2 \NR
\NC Poster \NC $\times$ 13 \NR
\NC Participant List \NC $\times$ 1 \NR
\HL
\stoptabulate

\subsection{Rundown of Function}

\setupTABLE[c][1][width=1.25in]
\setupTABLE[c][2][width=3.5in]
\setupTABLE[c][3][width=1.25in]
\bTABLE
\bTABLEhead

\bTR\bTH    \bf{Time}
\eTH\bTH    \bf{Description}
\eTH\bTH    \bf{PIC(s)}
\eTH\eTR

\eTABLEhead
\bTABLEbody

\bTR\bTD 17:00\endash18:00
\eTD\bTD Set Up Venue.
\eTD\bTD All
\eTD\eTR

\bTR\bTD 18:15\endash18:50
\eTD\bTD Registration.
\eTD\bTD Any 3
\eTD\eTR

\bTR\bTD 18:50\endash18:55
\eTD\bTD Welcoming Speech.
\eTD\bTD Any 2
\eTD\eTR

\bTR\bTD 18:55\endash19:00
\eTD\bTD Department Head Speech.
\eTD\bTD Any 2
\eTD\eTR

\bTR\bTD 19:00\endash20:30
\eTD\bTD Dinner.
\eTD\bTD All
\eTD\eTR

\bTR\bTD 19:30\endash20:00
\eTD\bTD Lucky Draw.
\eTD\bTD Any 4
\eTD\eTR

\bTR\bTD 20:30\endash20:35
\eTD\bTD Take Photos.
\eTD\bTD All
\eTD\eTR

\bTR\bTD 20:35\endash21:00
\eTD\bTD Clean Up.
\eTD\bTD All
\eTD\eTR

\eTABLEbody
\eTABLE

\subsection{Remarks}
\startitemize
\item Special arrangement during Inclement Weather or emergency: \\
If any of the Rainstorm Warnings or Tropical Cyclone Warning Signal No.3 or above is hoisted, the function will be either postponed or canceled. Participants will be notified of further arrangements through email.
\item There will be no available seating plan.
\item Confirm lucky draw and if alcohol beverages are acceptable.
\item Identity checks are needed before walk-ins are allowed.
\stopitemize

\pagebreak
