\startsection[title={CSESS Annual General Meeting}][
date={\date[d=10, m=3, y=2024][event]},
pic={Terry (P), Nelson (IV), Sam (EV), Samuel (In Sec), Stan (E Sec)}]

\subsection{Main PIC(s)}
\namedstructureuservariable{section}{pic}

\subsection{Objectives}
\startitemize
\item To review on the Cabinet of CSESS, HKUSTSU, 23\endash24.
\item To approve the financial reports submitted by the current Financial Secretary.
\item To provide the public with an opportunity to better understand the Elected Cabinet of CSESS, HKUST, 24\endash25.
\item To allow Society Members provide advice to the Elected Cabinet of CSESS, HKUST, 24\endash25.
\stopitemize

\subsection{Details}
\starttabulate[|rB|l|]
\NC Date
\NC \namedstructureuservariable{section}{date} \NR
\NC Time
\NC 18:00\endash21:00 \NR
\NC Venue
\NC Online \NR
\NC Audience
\NC All Members \NR
\NC Est. Participants
\NC 30 \NR
\NC Fee (\$)
\NC N/A \NR
\stoptabulate

\subsection{Schedule}

\setupTABLE[c][1][width=0.75in]
\setupTABLE[c][2][width=1in]
\setupTABLE[c][3][width=3in]
\setupTABLE[c][4][width=1.25in]
\bTABLE
\bTABLEhead

\bTR\bTH    \bf{DTF}
\eTH\bTH    \bf{Finish Date}
\eTH\bTH    \bf{Task}
\eTH\bTH    \bf{PIC(s)}
\eTH\eTR

\eTABLEhead
\bTABLEbody

\bTR\bTD 4\endash1
\eTD\bTD 15\high{th} February
\eTD\bTD Book Venue.
\eTD\bTD Stan (E Sec)
\eTD\eTR

\bTR\bTD 50\endash30
\eTD\bTD 25\high{th} February
\eTD\bTD Prepare Annual Report.
\eTD\bTD Terry (P) \\ Nelson (IV) \\ Sam (EV)
\eTD\eTR

\bTR\bTD 50\endash30
\eTD\bTD 1\high{st} March
\eTD\bTD Prepare Financial Report.
\eTD\bTD Paddy (Fin Sec)
\eTD\eTR

\bTR\bTD 4\endash2
\eTD\bTD 3\high{rd} March
\eTD\bTD Prepare Poster.
\eTD\bTD Cindy (PP Sec)
\eTD\eTR

\bTR\bTD 1
\eTD\bTD 3\high{rd} March
\eTD\bTD Buy Materials.
\eTD\bTD Nelson (IV) \\ Stan (E Sec)
\eTD\eTR

\bTR\bTD 7\endash1
\eTD\bTD 4\high{th} March
\eTD\bTD Promote.
\eTD\bTD Samuel (In Sec)
\eTD\eTR

\bTR\bTD 4\endash2
\eTD\bTD 4\high{th} March
\eTD\bTD Prepare Agenda.
\eTD\bTD Samuel (In Sec)
\eTD\eTR

\bTR\bTD 4\endash2
\eTD\bTD 4\high{th} March
\eTD\bTD Prepare Floor Plan.
\eTD\bTD Stan (E Sec)
\eTD\eTR

\eTABLEbody
\eTABLE

\subsubsection{Equipment \& Consumables}
\starttabulate[|l|l|]
\NC\setff{smallcaps}Equipment\NC\NR
\HL
\NC Wireless Microphones \NC $\times$ 2 \NR
\NC Camera \NC $\times$ 1 \NR
\NC Laptops \NC $\times$ 2 \NR
\NC Agenda \NC $\times$ 20 \NR
\HL
\NR
\NC\setff{smallcaps}Consumables\NC\NR
\HL
\NC Pens \NC $\times$ 10 \NR
\NC Draft Paper \NC $\times$ 30 \NR
\HL
\stoptabulate

\subsection{Rundown of Function}

\setupTABLE[c][1][width=1.25in]
\setupTABLE[c][2][width=3.5in]
\setupTABLE[c][3][width=1.25in]
\bTABLE
\bTABLEhead

\bTR\bTH    \bf{Time}
\eTH\bTH    \bf{Description}
\eTH\bTH    \bf{PIC(s)}
\eTH\eTR

\eTABLEhead
\bTABLEbody

\bTR\bTD 18:00\endash18:30
\eTD\bTD Set Up Venue.
\eTD\bTD Cindy (PP Sec) \\ Jacky (A Sec)
\eTD\eTR

\bTR\bTD 18:00\endash18:30
\eTD\bTD Set Up Streaming Equipment.
\eTD\bTD Samuel (In Sec) \\ Stan (E Sec)
\eTD\eTR

\bTR\bTD 18:30\endash18:35
\eTD\bTD Welcome Participants and Distribute Agenda.
\eTD\bTD Nelson (IV) \\ Sam (EV)
\eTD\eTR

\bTR\bTD 18:35\endash18:50
\eTD\bTD Receive and Adopt the Annual Report.
\eTD\bTD Terry (P)
\eTD\eTR

\bTR\bTD 18:50\endash19:05
\eTD\bTD Receive and Adopt the Financial Report.
\eTD\bTD Paddy (Fin Sec)
\eTD\eTR

\bTR\bTD 19:05\endash19:15
\eTD\bTD Discuss to have non-confidence with Executive Committee and announce the Honorary Member(s).
\eTD\bTD All
\eTD\eTR

\bTR\bTD 19:15\endash20:00
\eTD\bTD Introduce the Executive Committee of the next session.
\eTD\bTD All
\eTD\eTR

\bTR\bTD 20:00\endash20:30
\eTD\bTD Pass and approve year plan and financial budget of the next session.
\eTD\bTD Terry (P) \\ Paddy (Fin Sec)
\eTD\eTR

\bTR\bTD 20:30\endash20:45
\eTD\bTD Pass amendments to the Constitutions and appoint Honorary Auditor.
\eTD\bTD Nelson (IV)
\eTD\eTR

\bTR\bTD 20:45\endash21:00
\eTD\bTD Buffering time.
\eTD\bTD N/A
\eTD\eTR

\eTABLEbody
\eTABLE

\subsection{Remarks}
\startitemize
\item Special arrangement during Inclement Weather or emergency: \\
If any of the Rainstorm Warnings or Tropical Cyclone Warning Signal No.3 or above is hoisted, the function will be either postponed or canceled. Participants will be notified of further arrangements through email.
\item For the Elected Cabinet of CSESS, HKUSTSU, Session 2024\endash2025, and The Executive Committee of CSESS, HKUSTSU, Session 2023\endash2024, formal dressing is required.
\stopitemize

\stopsection
\pagebreak
