\section{Daily Operation of CSESS}

\subsection{General Promotion}
Promote functions to all target participants.

\subsubsection{Schedule}

\setupTABLE[c][1][width=1.25in]
\setupTABLE[c][2][width=3.5in]
\setupTABLE[c][3][width=1.25in]
\bTABLE
\bTABLEhead

\bTR\bTH \bold{DTF}
\eTH\bTH \bold{Task}
\eTH\bTH \bold{PIC(s)}
\eTH\eTR

\eTABLEhead
\bTABLEbody

\bTR\bTD 14, 1
\eTD\bTD Social Media Promotion Design (Facebook, Instagram).
\eTD\bTD Terry (P) \\ Stan (E Sec)
\eTD\eTR

\bTR\bTD 14, 1
\eTD\bTD Social Media Promotion Posting (Facebook, Instagram).
\eTD\bTD Nelson (IV) \\ Sam (EV)
\eTD\eTR

\bTR\bTD 14, 1
\eTD\bTD Discord Announcement.
\eTD\bTD Samuel (In Sec)
\eTD\eTR

\bTR\bTD 14, 1
\eTD\bTD Instant Messages (WhatsApp, Telegram, Signal).
\eTD\bTD All
\eTD\eTR

\bTR\bTD 14
\eTD\bTD CSESS Counter (LG5).
\eTD\bTD All
\eTD\eTR

\bTR\bTD 14
\eTD\bTD Event Promotion on CSESS Website.
\eTD\bTD Jacky (A Sec)
\eTD\eTR

\bTR\bTD 14, 7, 1
\eTD\bTD Mass Email to CSESS Members.
\eTD\bTD Samuel (In Sec)
\eTD\eTR

\eTABLEbody
\eTABLE

\subsection{Poster Promotion}
To promote functions through posters posted in designated areas of the campus.

\subsubsection{Date}
14 (DTF)

\subsubsection{Location}
\startitemize
\item Atrium, Area C
\item Bus Stop
\item Common Room 2466
\item G/F, Inner Wall of the Piazza, Near the Main Entrance of the Sports Hall
\item G/F, New Hall (Seafront Restaurant) ($\times$ 3)
\item G/F, Wall Adjacent to the Main Entrance of the Sports Hall
\item LG5, Lift 10\endash12
\item LG5, near escalator
\item LG7, Wall adjacent to the Canteen
\item The 2nd right wall of \quotation{Fong Shu Chuen Promenade} ({\switchtobodyfont[sourcehan]方樹泉廊})
\item The 3rd Pair of Pillars of Bridge-Link (Counted From LG5) ($\times$ 2)
\item 1/F, Lift 17\endash18, Both Sides
\item 10/F, Lift Lobby, UG Hall I
\stopitemize

\subsubsection{Schedule}

\setupTABLE[c][1][width=1.25in]
\setupTABLE[c][2][width=3.5in]
\setupTABLE[c][3][width=1.25in]
\bTABLE
\bTABLEhead

\bTR\bTH    \bf{DTF}
\eTH\bTH    \bf{Task}
\eTH\bTH    \bf{PIC(s)}
\eTH\eTR

\eTABLEhead
\bTABLEbody

\bTR\bTD 28\endash16
\eTD\bTD Design Poster.
\eTD\bTD Cindy (PP Sec)
\eTD\eTR

\bTR\bTD 15
\eTD\bTD Society Chop.
\eTD\bTD Any 1
\eTD\eTR

\bTR\bTD 14
\eTD\bTD Post Poster.
\eTD\bTD Nelson (IV) \\ Stan (E Sec)
\eTD\eTR

\eTABLEbody
\eTABLE

\subsubsection{Equipment \& Consumables}
\starttabulate[|l|l|]
\NC\setff{smallcaps}Equipment\NC\NR
\HL
\NC Scissors    \NC $\times$ 1  \NR
\HL
\NR
\NC\setff{smallcaps}Consumables\NC\NR
\HL
\NC Poster      \NC $\times$ 16 \NR
\NC Tape        \NC $\times$ 1  \NR
\HL
\stoptabulate

\subsubsection{Remarks}
Expiry date must be printed on the poster. The expiry date is at most 14 days after posting.

\subsection{CSESS Counter Promotion}
To promote functions by holding an on-campus or virtual online counter.

\subsubsection{Date}
14\endash1 (DTF)

\subsubsection{Location}
LG5

\subsubsection{Schedule}

\setupTABLE[c][1][width=1.25in]
\setupTABLE[c][2][width=3.5in]
\setupTABLE[c][3][width=1.25in]
\bTABLE
\bTABLEhead

\bTR\bTH    \bf{DTF}
\eTH\bTH    \bf{Task}
\eTH\bTH    \bf{PIC(s)}
\eTH\eTR

\eTABLEhead
\bTABLEbody

\bTR\bTD 20\endash15
\eTD\bTD Prepare Equipment and Materials for Counter.
\eTD\bTD Any 3
\eTD\eTR

\bTR\bTD 14
\eTD\bTD Sit in the Counter.
\eTD\bTD All
\eTD\eTR

\eTABLEbody
\eTABLE

\subsubsection{Equipment}
\starttabulate[|l|l|]
\NC\setff{smallcaps}Equipment\NC\NR
\HL
\NC Scissors            \NC $\times$ 1  \NR
\NC Society Signboard   \NC $\times$ 1  \NR
\NC Tablecloth          \NC $\times$ 1  \NR
\NC Laptop              \NC $\times$ 1  \NR
\NC Money Box           \NC $\times$ 1  \NR
\NC Receipt Book        \NC $\times$ 1  \NR
\NC Cable Reel          \NC $\times$ 1  \NR
\NC Event Poster Board  \NC $\times$ 1  \NR
\HL
\stoptabulate

\pagebreak
