\startsection[title={CSESS Rock Climbing Day}][
date={\date[d=25, m=11, y=2023][event]},
pic={Nelson (IV), Sam (EV)}]

\subsection{Main PIC(s)}
\namedstructureuservariable{section}{pic}

\subsection{Objectives}
\startitemize
\item To promote healthy lifestyle among CSE students.
\item To offer a chance for students to relax by taking part in sports, after the three years of lockdown due to the pandemic.
\item Provide a chance for CSE students to connect with each other.
\stopitemize

\subsection{Details}
\starttabulate[|rB|l|]
\NC Date
\NC \namedstructureuservariable{section}{date} \NR
\NC Time
\NC 12:00\endash18:00 \NR
\NC Venue
\NC Kizuna Climbing Gym (TKO) \NR
\NC Audience
\NC CSE Students and CSESS Members \NR
\NC Est. Participants
\NC 20 (Excluding Excos) \NR
\NC Fee (\$)
\NC 80 \NR
\NC Budget (\$)
\NC 200@1 \NR
\stoptabulate

\subsection{Schedule}

\setupTABLE[c][1][width=0.75in]
\setupTABLE[c][2][width=1in]
\setupTABLE[c][3][width=3in]
\setupTABLE[c][4][width=1.25in]
\bTABLE
\bTABLEhead

\bTR\bTH    \bf{DTF}
\eTH\bTH    \bf{Finish Date}
\eTH\bTH    \bf{Task}
\eTH\bTH    \bf{PIC(s)}
\eTH\eTR

\eTABLEhead
\bTABLEbody

\bTR\bTD N/A
\eTD\bTD 15\high{th} March
\eTD\bTD Confirm Details with Rock Climbing.
\eTD\bTD Nelson (IV)
\eTD\eTR

\bTR\bTD N/A
\eTD\bTD 15\high{th} March
\eTD\bTD Confirm with Boulder Gym.
\eTD\bTD Nelson (IV)
\eTD\eTR

\bTR\bTD N/A
\eTD\bTD 15\high{th} March
\eTD\bTD Confirm Human Resources with Rock Climbing.
\eTD\bTD Nelson (IV)
\eTD\eTR

\bTR\bTD 2
\eTD\bTD 20\high{th} March
\eTD\bTD Discuss with Boulder Gym.
\eTD\bTD Nelson (IV)
\eTD\eTR

\bTR\bTD 14
\eTD\bTD Two Weeks Before
\eTD\bTD Design Poster.
\eTD\bTD Cindy (PP Sec)
\eTD\eTR

\bTR\bTD 7\endash1
\eTD\bTD One Week Before
\eTD\bTD Post Poster.
\eTD\bTD Nelson (IV)
\eTD\eTR

\eTABLEbody
\eTABLE

\pagebreak
\subsection{Equipment}
\starttabulate[|l|l|]
\NC\setff{smallcaps}Equipment\NC\NR
\HL
\NC Society Signboard   \NC $\times$ 1  \NR
\HL
\stoptabulate

\subsection{Rundown of Function}

\setupTABLE[c][1][width=1.25in]
\setupTABLE[c][2][width=3.5in]
\setupTABLE[c][3][width=1.25in]
\bTABLE
\bTABLEhead

\bTR\bTH    \bf{Time}
\eTH\bTH    \bf{Description}
\eTH\bTH    \bf{PIC(s)}
\eTH\eTR

\eTABLEhead
\bTABLEbody

\bTR\bTD 12:00
\eTD\bTD Assemble on Campus.
\eTD\bTD Nelson (IV)
\eTD\eTR

\bTR\bTD 12:00\endash13:00
\eTD\bTD Travel to Boulder Gym.
\eTD\bTD Nelson (IV)
\eTD\eTR

\bTR\bTD 13:00\endash18:00
\eTD\bTD Boulder Tutorial \& Free Time at Boulder Gym.
\eTD\bTD Nelson (IV)
\eTD\eTR

\eTABLEbody
\eTABLE

\subsection{Remarks}
\startitemize
\item Special arrangement during Inclement Weather or emergency: \\
If any of the Rainstorm Warnings or Tropical Cyclone Warning Signal No.3 or above is hoisted, the function will be either postponed or canceled. Participants will be notified of further arrangements through email.
\stopitemize

\stopsection
\pagebreak
