\startsection[title={CSE Farewell Video}][
date={\date[d=2, m=5, y=2023][event]},
pic={Nelson (IV), Stan (E Sec), Jacky (A Sec)}]

\subsection{Main PIC(s)}
\namedstructureuservariable{section}{pic}

\subsection{Objectives}
\startitemize
\item To celebrate the graduation of CSE graduates.
\item To provide reminiscence comfort for final year CSE students.
\item To recollect and gather the past memories of the graduates.
\stopitemize

\subsection{Details}
\starttabulate[|rB|l|]
\NC Date
\NC \namedstructureuservariable{section}{date} \NR
\NC Time
\NC 12:00 \NR
\NC Venue
\NC Instagram and YouTube \NR
\NC Audience
\NC Graduates and CSE Staff \NR
\NC Est. Participants
\NC All CSE Graduates \NR
\stoptabulate

\subsection{Schedule}

\setupTABLE[c][1][width=0.75in]
\setupTABLE[c][2][width=1in]
\setupTABLE[c][3][width=3in]
\setupTABLE[c][4][width=1.25in]
\bTABLE
\bTABLEhead

\bTR\bTH    \bf{DTF}
\eTH\bTH    \bf{Finish Date}
\eTH\bTH    \bf{Task}
\eTH\bTH    \bf{PIC(s)}
\eTH\eTR

\eTABLEhead
\bTABLEbody

\bTR\bTD 20
\eTD\bTD 11\high{th} April
\eTD\bTD Contact Professors.
\eTD\bTD Jacky (A Sec)
\eTD\eTR

\bTR\bTD 24\endash15
\eTD\bTD 14\high{th} April
\eTD\bTD Draft Farewell Video.
\eTD\bTD Nelson (IV) \\ Stan (E Sec)
\eTD\eTR

\bTR\bTD 14\endash10
\eTD\bTD 15\high{th} April
\eTD\bTD Film Footage.
\eTD\bTD Nelson (IV) \\ Jacky (A Sec)
\eTD\eTR

\bTR\bTD 10\endash4
\eTD\bTD 21\high{st} April
\eTD\bTD Edit Video.
\eTD\bTD Nelson (IV) \\ Jacky (A Sec)
\eTD\eTR

\bTR\bTD 14\endash1
\eTD\bTD 25\high{th} April
\eTD\bTD Promote.
\eTD\bTD N/A
\eTD\eTR

\eTABLEbody
\eTABLE

\pagebreak
\subsection{Equipment \& Consumables}
\starttabulate[|l|l|]
\NC\setff{smallcaps}Equipment\NC\NR
\HL
\NC Camera          \NC $\times$ 1  \NR
\NC Laptop          \NC $\times$ 1  \NR
\NC Tripod          \NC $\times$ 1  \NR
\NC Camera Battery  \NC $\times$ 1  \NR
\NC Camera Charger  \NC $\times$ 1  \NR
\NC Laptop Charger  \NC $\times$ 1  \NR
\NC SD Card         \NC $\times$ 1  \NR
\HL
\NR
\NC\setff{smallcaps}Consumables\NC\NR
\HL
\NC Filming Props   \NC $\times$ 16 \NR
\HL
\stoptabulate

\subsection{Rundown of Function (Filming Day)}

\setupTABLE[c][1][width=1.25in]
\setupTABLE[c][2][width=3.5in]
\setupTABLE[c][3][width=1.25in]
\bTABLE
\bTABLEhead

\bTR\bTH    \bf{Time}
\eTH\bTH    \bf{Description}
\eTH\bTH    \bf{PIC(s)}
\eTH\eTR

\eTABLEhead
\bTABLEbody

\bTR\bTD 10:00\endash10:10
\eTD\bTD Gather Presenting Executive Committee Members.
\eTD\bTD N/A
\eTD\eTR

\bTR\bTD 10:10\endash18:00
\eTD\bTD Film Footage.
\eTD\bTD Nelson (IV) \\ Jacky (A Sec)
\eTD\eTR

\eTABLEbody
\eTABLE

\subsection{Remarks}
\startitemize
\item Special arrangement during Inclement Weather or emergency: \\
If any of the Rainstorm Warnings or Tropical Cyclone Warning Signal No.3 or above is hoisted, the function will be either postponed or canceled. Participants will be notified of further arrangements through email.
\stopitemize

\stopsection
\pagebreak
