\startsection[title={CSE Farewell Dinner}][
date={\date[d=10, m=5, y=2023][event]},
pic={Terry (P), Jacky (A Sec)}]

\subsection{Main PIC(s)}
\namedstructureuservariable{section}{pic}

\subsection{Objectives}
\startitemize
\item To celebrate the achievements of the graduating class and recognize their hard work and dedication.
\item To honor and give thanks to the faculty, staff, and mentors who have supported the graduates throughout their academic journey.
\item To have fun and enjoy good food, entertainment, and company in a relaxed and festive atmosphere.
\stopitemize

\subsection{Details}
\starttabulate[|rB|l|]
\NC Date
\NC \namedstructureuservariable{section}{date} \NR
\NC Time
\NC 18:30\endash20:30 \NR
\NC Venue
\NC UC Bistro \NR
\NC Audience
\NC Graduates and CSE Staff \NR
\NC Est. Participants
\NC 70\endash80 \NR
\NC Fee (\$)
\NC Sponsored by CSE Department \NR
\NC Budget (\$)
\NC 8000 \NR
\NC Dress Code
\NC Smart Casual \NR
\stoptabulate

\subsection{Schedule}

\setupTABLE[c][1][width=0.75in]
\setupTABLE[c][2][width=1in]
\setupTABLE[c][3][width=3in]
\setupTABLE[c][4][width=1.25in]
\bTABLE
\bTABLEhead

\bTR\bTH    \bf{DTF}
\eTH\bTH    \bf{Finish Date}
\eTH\bTH    \bf{Task}
\eTH\bTH    \bf{PIC(s)}
\eTH\eTR

\eTABLEhead
\bTABLEbody

\bTR\bTD N/A
\eTD\bTD 11\high{th} April
\eTD\bTD Confirm Details with CSE Department.
\eTD\bTD Jacky (A Sec)
\eTD\eTR

\bTR\bTD N/A
\eTD\bTD 11\high{th} April
\eTD\bTD Check Equipment and Material with CSE Department.
\eTD\bTD Jacky (A Sec)
\eTD\eTR

\bTR\bTD 1
\eTD\bTD 11\high{th} April
\eTD\bTD Book Venue.
\eTD\bTD Jacky (A Sec)
\eTD\eTR

\bTR\bTD 1
\eTD\bTD 25\high{th} April
\eTD\bTD Remind CSE Department to Send Email.
\eTD\bTD Jacky (A Sec)
\eTD\eTR

\bTR\bTD 10, 1
\eTD\bTD 25\high{th} April
\eTD\bTD Design Guest Book, Photo Props and Poster.
\eTD\bTD Samuel (In Sec) \\ Cindy (PP Sec) \\ Jacky (A Sec)
\eTD\eTR

\bTR\bTD 10, 1
\eTD\bTD 25\high{th} April
\eTD\bTD Buy Nametags and Boutonnière.
\eTD\bTD Samuel (In Sec) \\ Cindy (PP Sec) \\ Jacky (A Sec)
\eTD\eTR

\bTR\bTD 1
\eTD\bTD 25\high{th} April
\eTD\bTD Print Poster and Stick Poster.
\eTD\bTD Stan (E Sec)
\eTD\eTR

\eTABLEbody
\eTABLE

\subsection{Equipment \& Consumables}
\starttabulate[|l|l|]
\NC\setff{smallcaps}Equipment\NC\NR
\HL
\NC Backdrop            \NC $\times$ 1  \NR
\NC Boutonnière         \NC $\times$ 20 \NR
\NC Cameras             \NC $\times$ 2  \NR
\NC Farewell Video      \NC $\times$ 1  \NR
\NC Guest Book          \NC $\times$ 1  \NR
\NC Nametags            \NC $\times$ 20 \NR
\NC Notice Boards       \NC $\times$ 2  \NR
\NC Pens                \NC $\times$ 2  \NR
\NC Photo Props         \NC $\times$ 7  \NR
\NC Society Signboard   \NC $\times$ 1  \NR
\NC Paper               \NC $\times$ 100\NR
\NC Mics                \NC $\times$ 4  \NR
\HL
\NR
\NC\setff{smallcaps}Consumables\NC\NR
\HL
\NC Graduate Souvenirs  \NC $\times$ 80 \NR
\NC Greeting Cards      \NC $\times$ 80 \NR
\NC Letter Balloons     \NC $\times$ 17 \NR
\NC Lucky Draw Gifts    \NC $\times$ 4  \NR
\NC Lucky Draw Box      \NC $\times$ 1  \NR
\NC Participant List    \NC $\times$ 1  \NR
\NC Posters             \NC $\times$ 13 \NR
\NC Scissors            \NC $\times$ 2  \NR
\NC Tape                \NC $\times$ 2  \NR
\HL
\stoptabulate

\pagebreak
\subsection{Rundown of Function}

\setupTABLE[c][1][width=1.25in]
\setupTABLE[c][2][width=3.5in]
\setupTABLE[c][3][width=1.25in]
\bTABLE
\bTABLEhead

\bTR\bTH    \bf{Time}
\eTH\bTH    \bf{Description}
\eTH\bTH    \bf{PIC(s)}
\eTH\eTR

\eTABLEhead
\bTABLEbody

\bTR\bTD 17:00\endash18:00
\eTD\bTD Set Up Venue.
\eTD\bTD All
\eTD\eTR

\bTR\bTD 18:15\endash18:50
\eTD\bTD Registration.
\eTD\bTD Any 3
\eTD\eTR

\bTR\bTD 18:50\endash18:55
\eTD\bTD CSESS Welcome Speech.
\eTD\bTD Any 2
\eTD\eTR

\bTR\bTD 18:55\endash19:00
\eTD\bTD CSE Department Head Speech.
\eTD\bTD Any 2
\eTD\eTR

\bTR\bTD 19:00\endash20:30
\eTD\bTD Dinner.
\eTD\bTD All
\eTD\eTR

\bTR\bTD 19:30\endash20:00
\eTD\bTD Lucky Draw.
\eTD\bTD Any 4
\eTD\eTR

\bTR\bTD 20:25\endash20:30
\eTD\bTD Photo.
\eTD\bTD All
\eTD\eTR

\bTR\bTD 20:35\endash21:00
\eTD\bTD Clean Up.
\eTD\bTD All
\eTD\eTR

\eTABLEbody
\eTABLE

\subsection{Remarks}
\startitemize
\item Special arrangement during Inclement Weather or emergency: \\
If any of the Rainstorm Warnings or Tropical Cyclone Warning Signal No.3 or above is hoisted, the function will be either postponed or canceled. Participants will be notified of further arrangements through email.
\item There will be no available seating plan.
\item Confirm lucky draw and if alcohol beverages are acceptable.
\item Identity checks are needed before walk-ins are allowed.
\stopitemize

\stopsection
\pagebreak
