\startsection[title={CSE Welcome Day}][
date={\date[d=15, m=7, y=2023][event]},
pic={Samuel (In Sec), Stan (E Sec)}]

\subsection{Main PIC(s)}
\namedstructureuservariable{section}{pic}

\subsection{Objectives}
\startitemize
\item To relieve stress of new students by offering fun water games.
\item To create bonding between new students and CSESS Members, and provide an opportunity for new students to meet their peers.
\item To introduce the Society and the Executive Committee to new students.
\stopitemize

\subsection{Details}
\starttabulate[|rB|l|]
\NC Date
\NC \namedstructureuservariable{section}{date} \NR
\NC Time
\NC 10:00\endash20:00 \NR
\NC Venue
\NC Clear Water Bay, First Beach \NR
\NC Audience
\NC Undergraduates Who Recently Declared a Major Offered by the CSE Department \NR
\NC Est. Participants
\NC 30 \NR
\NC Budget (\$)
\NC 300 \NR
\NC Fee (\$)
\NC 40 (Members), 60 (Non-Members) \NR
\stoptabulate

\subsection{Schedule}

\setupTABLE[c][1][width=0.75in]
\setupTABLE[c][2][width=1in]
\setupTABLE[c][3][width=3in]
\setupTABLE[c][4][width=1.25in]
\bTABLE
\bTABLEhead

\bTR\bTH    \bf{DTF}
\eTH\bTH    \bf{Finish Date}
\eTH\bTH    \bf{Task}
\eTH\bTH    \bf{PIC(s)}
\eTH\eTR

\eTABLEhead
\bTABLEbody

\bTR\bTD 21\endash1
\eTD\bTD 15\high{th} June
\eTD\bTD Ask CSE Department for Funding.
\eTD\bTD Jacky (A Sec)
\eTD\eTR

\bTR\bTD 7\endash2
\eTD\bTD 18\high{th} June
\eTD\bTD Design Poster.
\eTD\bTD Cindy (PP Sec)
\eTD\eTR

\bTR\bTD 7\endash2
\eTD\bTD 18\high{th} June
\eTD\bTD Design Games.
\eTD\bTD Stan (E Sec) \\ Paddy (Fin Sec)
\eTD\eTR

\bTR\bTD 14\endash1
\eTD\bTD 22\high{nd} June
\eTD\bTD Promote.
\eTD\bTD Samuel (In Sec)
\eTD\eTR

\bTR\bTD 14\endash1
\eTD\bTD 22\high{nd} June
\eTD\bTD Contact All Undergraduates Who Recently Declared a Major Offered by the CSE Department.
\eTD\bTD Samuel (In Sec) \\ Stan (E Sec)
\eTD\eTR

\bTR\bTD 7\endash1
\eTD\bTD 28\high{th} June
\eTD\bTD Rehearse Games.
\eTD\bTD All
\eTD\eTR

\bTR\bTD 7\endash1
\eTD\bTD 10\high{th} July
\eTD\bTD Prepare Foods and Equipments for Barbeque.
\eTD\bTD All
\eTD\eTR

\bTR\bTD 7\endash1
\eTD\bTD 13\high{th} July
\eTD\bTD Send Out Final Reminders to Participants.
\eTD\bTD Nelson (IV)
\eTD\eTR

\eTABLEbody
\eTABLE

\subsection{Equipment \& Consumables}
\starttabulate[|l|l|]
\NC\setff{smallcaps}Equipment\NC\NR
\HL
\NC Camera                  \NC $\times$ 1  \NR
\NC Thermal Boxes           \NC $\times$ 2  \NR
\NC Society Banner          \NC $\times$ 1  \NR
\NC Water Blasters          \NC $\times$ 40 \NR
\NC Large Beach Buckets     \NC $\times$ 4  \NR
\NC Small Beach Buckets     \NC $\times$ 4  \NR
\HL
\NR
\NC\setff{smallcaps}Consumables\NC\NR
\HL
\NC Barbeque Meal for One Person \NC $\times$ 40  \NR
\NC Barbeque Fork \NC $\times$ 40  \NR
\NC Barbeque Net \NC $\times$ 4  \NR
\NC Newspaper \NC $\times$ 4  \NR
\NC Charcoal Bags \NC $\times$ 4  \NR
\NC Drinks \NC 60 $\times$ 330ml  \NR
\NC Honey Jars \NC $\times$ 3  \NR
\NC Lighter \NC $\times$ 2  \NR
\NC Participant List \NC $\times$ 1  \NR
\NC Plastic Cups \NC $\times$ 60  \NR
\NC Plastic Gloves \NC $\times$ 50  \NR
\NC Plate and Utensil \NC $\times$ 75  \NR
\NC Tissue (Boxes) \NC $\times$ 5  \NR
\NC Tongs \NC $\times$ 4  \NR
\NC Trash Bags \NC $\times$ 5  \NR
\NC White Bread (Loaves) \NC $\times$ 3  \NR
\NC Working Gloves \NC $\times$ 4  \NR
\HL
\stoptabulate

\subsection{Rundown of Function}

\setupTABLE[c][1][width=1.25in]
\setupTABLE[c][2][width=3.5in]
\setupTABLE[c][3][width=1.25in]
\bTABLE[split=no]
\bTABLEhead

\bTR\bTH    \bf{Time}
\eTH\bTH    \bf{Description}
\eTH\bTH    \bf{PIC(s)}
\eTH\eTR

\eTABLEhead
\bTABLEbody

\bTR\bTD 10:00\endash12:00
\eTD\bTD Prepare Venue.
\eTD\bTD Any 2
\eTD\eTR

\bTR\bTD 10:00\endash12:00
\eTD\bTD Hold Barbeque Stove.
\eTD\bTD Any 2
\eTD\eTR

\bTR\bTD 12:00\endash12:30
\eTD\bTD Meet Up at the North Gate, and at Diamond Hill Station.
\eTD\bTD Any 4
\eTD\eTR

\bTR\bTD 12:30\endash13:30
\eTD\bTD Travel To Clear Water Bay, First Beach.
\eTD\bTD Any 4
\eTD\eTR

\bTR\bTD 13:30\endash13:45
\eTD\bTD Introduction.
\eTD\bTD Terry (P) \\ Any 2 MCs
\eTD\eTR

\bTR\bTD 13:45\endash14:15
\eTD\bTD Icebreaking Games.
\eTD\bTD N/A
\eTD\eTR

\bTR\bTD 14:15\endash14:50
\eTD\bTD Group Games.
\eTD\bTD Any 6
\eTD\eTR

\bTR\bTD 14:50\endash15:00
\eTD\bTD Break.
\eTD\bTD N/A
\eTD\eTR

\bTR\bTD 15:00\endash15:45
\eTD\bTD Mass Games.
\eTD\bTD Any 6
\eTD\eTR

\bTR\bTD 15:45\endash16:05
\eTD\bTD Photo-taking.
\eTD\bTD N/A
\eTD\eTR

\bTR\bTD 16:05\endash16:30
\eTD\bTD Set Up Barbeque Sites.
\eTD\bTD Any 2
\eTD\eTR

\bTR\bTD 16:30\endash19:00
\eTD\bTD Barbeque.
\eTD\bTD All
\eTD\eTR

\bTR\bTD 19:00\endash20:00
\eTD\bTD Clean Up.
\eTD\bTD All
\eTD\eTR

\eTABLEbody
\eTABLE

\subsection{Remarks}
\startitemize
\item Special arrangement during Inclement Weather or emergency: \\
If any of the Rainstorm Warnings or Tropical Cyclone Warning Signal No.3 or above is hoisted, the function will be either postponed or canceled. Participants will be notified of further arrangements through email.
\item There will be both Chinese and English MCs if there are non cantonese speaking participants.
\item Some members might go on field trips one month before the activity day.
\item All participants are discouraged from entering the water.
\stopitemize

\stopsection
\pagebreak
