\startsection[title={CSESS Orientation Day}][
date={\date[d=13, m=8, y=2023][event]},
pic={Terry (P), Nelson (IV), Sam (EV)}]

\subsection{Main PIC(s)}
\namedstructureuservariable{section}{pic}

\subsection{Objectives}
\startitemize
\item To introduce the Society and the Executive Committee to new students.
\item To promote activities and welfare provided by the Society.
\item To help students to be more involved in the upcoming Orientation Camp.
\item To enable students who cannot participate in the Orientation Camp to meet like-minded friends.
\stopitemize

\subsection{Details}
\starttabulate[|rB|l|]
\NC Date
\NC \namedstructureuservariable{section}{date} \NR
\NC Time
\NC 13:30\endash18:00 \NR
\NC Venue
\NC Common Room 5+6 \NR
\NC Audience
\NC Participants of Orientation Camp \NR
\NC Est. Participants
\NC 40 (Freshmen) + 20 (Group Leaders) = 60 \NR
\NC Budget (\$)
\NC 300 \NR
\NC Fee (\$)
\NC 120 (Freshmen Member), 150 (Freshmen Non-Member), \NR
\NC \NC 30 (Group Leader Member), 50 (Group Leader Non-Member) \NR
\stoptabulate

\subsection{Schedule}

\setupTABLE[c][1][width=0.75in]
\setupTABLE[c][2][width=1in]
\setupTABLE[c][3][width=3in]
\setupTABLE[c][4][width=1.25in]
\bTABLE
\bTABLEhead

\bTR\bTH    \bf{DTF}
\eTH\bTH    \bf{Finish Date}
\eTH\bTH    \bf{Task}
\eTH\bTH    \bf{PIC(s)}
\eTH\eTR

\eTABLEhead
\bTABLEbody

\bTR\bTD 3\endash1
\eTD\bTD 10\high{th} July
\eTD\bTD Book venue.
\eTD\bTD Samuel (In Sec)
\eTD\eTR

\bTR\bTD 4\endash2
\eTD\bTD 15\high{th} July
\eTD\bTD Design Poster.
\eTD\bTD Cindy (PP Sec)
\eTD\eTR

\bTR\bTD 3\endash1
\eTD\bTD 20\high{th} July
\eTD\bTD Confirm Rundown Details.
\eTD\bTD Nelson (IV) \\ Sam (EV)
\eTD\eTR

\bTR\bTD 3\endash1
\eTD\bTD 20\high{th} July
\eTD\bTD Prepare Games.
\eTD\bTD Stan (E Sec) \\ Paddy (F Sec) \\ Jacky (A Sec)
\eTD\eTR

\bTR\bTD 4\endash2
\eTD\bTD 23\high{rd} July
\eTD\bTD Prepare Equipment.
\eTD\bTD Stan (E Sec) \\ Paddy (F Sec) \\ Jacky (A Sec)
\eTD\eTR

\bTR\bTD 1
\eTD\bTD 30\high{th} July
\eTD\bTD Final Rehearsal.
\eTD\bTD All
\eTD\eTR

\bTR\bTD 14\endash7\endash1
\eTD\bTD 4\high{th} August
\eTD\bTD Recruit Group Leader.
\eTD\bTD Nelson (IV) \\ Cindy (PP Sec)
\eTD\eTR

\bTR\bTD 14\endash7\endash1
\eTD\bTD 4\high{th} August
\eTD\bTD Promote.
\eTD\bTD Samuel (In Sec) \\ Cindy (PP Sec)
\eTD\eTR

\eTABLEbody
\eTABLE

\subsection{Equipment \& Consumables}
\starttabulate[|l|l|]
\NC\setff{smallcaps}Equipment\NC\NR
\HL
\NC Society Banner          \NC $\times$ 1  \NR
\NC Camera                  \NC $\times$ 1  \NR
\NC Pens                    \NC $\times$ 10 \NR
\HL
\NR
\NC\setff{smallcaps}Consumables\NC\NR
\HL
\NC Drinks                  \NC 8 $\times$ 8 $\times$ 330ml \NR
\NC Participant List        \NC $\times$ 1      \NR
\NC Tissue (Boxes)          \NC $\times$ 5      \NR
\NC Trash Bags              \NC $\times$ 5      \NR
\NC Paper                   \NC $\times$ 100    \NR
\NC Orientation Day T-Shirt \NC $\times$ 70     \NR
\HL
\stoptabulate

\subsection{Rundown of Function}

\setupTABLE[c][1][width=1.25in]
\setupTABLE[c][2][width=3.5in]
\setupTABLE[c][3][width=1.25in]
\bTABLE
\bTABLEhead

\bTR\bTH    \bf{Time}
\eTH\bTH    \bf{Description}
\eTH\bTH    \bf{PIC(s)}
\eTH\eTR

\eTABLEhead
\bTABLEbody

\bTR\bTD 12:45\endash13:30
\eTD\bTD Set Up Venue.
\eTD\bTD Any 4
\eTD\eTR

\bTR\bTD 13:30\endash13:45
\eTD\bTD Meet Up and Travel to Venue.
\eTD\bTD Any 4
\eTD\eTR

\bTR\bTD 13:45\endash14:00
\eTD\bTD Introduction and Divide in Groups.
\eTD\bTD All
\eTD\eTR

\bTR\bTD 14:00\endash14:30
\eTD\bTD Icebreaking (in Small Groups).
\eTD\bTD N/A
\eTD\eTR

\bTR\bTD 14:30\endash15:30
\eTD\bTD Mass Games.
\eTD\bTD All
\eTD\eTR

\bTR\bTD 15:30\endash17:00
\eTD\bTD School Hunt.
\eTD\bTD All
\eTD\eTR

\bTR\bTD 17:00\endash17:30
\eTD\bTD Chanting.
\eTD\bTD Any 2
\eTD\eTR

\bTR\bTD 17:30\endash18:00
\eTD\bTD Announce Winners.
\eTD\bTD All
\eTD\eTR

\bTR\bTD 18:00\endash18:30
\eTD\bTD Clean Up.
\eTD\bTD All
\eTD\eTR

\eTABLEbody
\eTABLE

\subsection{Remarks}
\startitemize
\item Special arrangement during Inclement Weather or emergency: \\
If any of the Rainstorm Warnings or Tropical Cyclone Warning Signal No.3 or above is hoisted, the function will be either postponed or canceled. Participants will be notified of further arrangements through email.
\item There will be both Chinese and English MCs if there are non cantonese speaking participants.
\stopitemize

\stopsection
\pagebreak
